quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-13 paper-quollr.Rmd
Added descriptions for glance function

@@

Users can pass data to `augment()` via either the `training_data` argument or the `newdata` argument. If data is passed to the `training_data` argument, it must be exactly the data that was used to fit the model.  Alternatively, datasets can be passed to `newdata` to augment data that was not used during model fitting. This requires that at least all predictor variable columns used to fit the model are present. If the original outcome variable used to fit the model is not included in `newdata`, then no corresponding column will be included in the output.

@@

>>>>

This function begins by renaming the columns of the input `model_highd` data frame to avoid naming conflicts during subsequent joins. It then uses the `predict_emb()` function to assign each point in the high-dimensional dataset to a corresponding bin in the 2D model, producing a prediction data frame that contains both the predicted bin assignment (`pred_hb_id`) and the original observation `ID`.

The function joins this prediction output with both the high-dimensional model (to get mean bin coordinates in the original space) and the original high-dimensional data (to retrieve true coordinates). It then calculates squared differences between the true and predicted high-dimensional coordinates for each dimension, storing these as `error_square_x1`, `error_square_x2`, ..., up to the dimensionality of the data.

From these per-dimension errors, the function computes absolute error which is the sum of absolute differences across all dimensions and observations and the Mean squared error (MSE) which is the average of the total squared error per point.

These metrics are returned in a tibble as `Error` (absolute error) and `MSE` (mean squared error).

@@

Users can pass data to `augment()` via either the `highd_data` argument. This requires that at least all predictor variable columns used to fit the model are present. If the original outcome variable used to fit the model is not included in `newdata`, then no corresponding column will be included in the output.

@@

### $2\text{-}D$ projection

### 2025-05-13 paper-quollr.tex
Added descriptions for glance function

@@

>>>>

This function begins by renaming the columns of the input \texttt{model\_highd} data frame to avoid naming conflicts during subsequent joins. It then uses the \texttt{predict\_emb()} function to assign each point in the high-dimensional dataset to a corresponding bin in the 2D model, producing a prediction data frame that contains both the predicted bin assignment (\texttt{pred\_hb\_id}) and the original observation \texttt{ID}.

The function joins this prediction output with both the high-dimensional model (to get mean bin coordinates in the original space) and the original high-dimensional data (to retrieve true coordinates). It then calculates squared differences between the true and predicted high-dimensional coordinates for each dimension, storing these as \texttt{error\_square\_x1}, \texttt{error\_square\_x2}, \ldots, up to the dimensionality of the data.

From these per-dimension errors, the function computes absolute error which is the sum of absolute differences across all dimensions and observations and the Mean squared error (MSE) which is the average of the total squared error per point.

These metrics are returned in a tibble as \texttt{Error} (absolute error) and \texttt{MSE} (mean squared error).

@@

\subsubsection{\texorpdfstring{\(2\text{-}D\) projection}{2\textbackslash text\{-\}D projection}}\label{text-d-projection}
